SVG: The Paper

### 2022-04-14 Analysis/index.Rmd
minor edits

Let's plot some examples oh highly predictable (top 5%), and unpredictable (bottom 5%) trials.

@@

@@

Here are some typical trials:

@@

plts[[1]] + plts[[2]] + plts[[3]]
```

>>>>

Let's plot some examples oh highly predictable (top 5%), typical (middle 10%) and unpredictable (bottom 5%) trials.

@@

We can see that for these highly predictable trials, we make very few mistakes, and those that we do make appear to be related to some sort of shortest-path optimization on the part of the participant.

@@

Here are some typical trials. Possible we have the path-length minimisation issue again.

@@
